MassWateR: Improving quality control, analysis, and sharing of water quality data

### 2023-07-09 paper.Rmd
flextable issue fixed by adding latex dependencies

---
title: "MassWateR: Improving quality control, analysis, and sharing of water quality data"
date: "`r Sys.Date()`"
abstract: >
  An abstract of less than 150 words.
draft: true
author:  
  # see ?rjournal_article for more information
  - name: Marcus W. Beck
    affiliation: Tampa Bay Estuary Program
    address:
    - 263 13th Ave S
    - St. Petersburg, Florida, USA 33701
    url: https://tbep.org
    orcid: 0000-0002-4996-0059
    email:  mbeck@tbep.org
  - name: Benjamen Wetherill
    url: https://www.acasak.com/
    email: bwetherill@acasak.co
    affiliation: ACASAK Consulting
    address:
    - Boston, Massachusetts, USA
    orcid: 0000-0002-0912-0225
  - name: Jillian Carr
    url: https://www.mass.gov/orgs/massachusetts-bays-national-estuary-partnership
    email: Jillian.Carr@umb.edu
    affiliation: Massachusetts Bays National Estuary Partnership
    address:
    - University of Massachusetts Boston, 100 Morrissey Blvd
    - Boston, Massachusetts, USA 02125
  - name: Pamela DiBona
    url: https://www.mass.gov/orgs/massachusetts-bays-national-estuary-partnership
    email: pamela.dibona@state.ma.us
    affiliation: Massachusetts Bays National Estuary Partnership
    address:
    - University of Massachusetts Boston, 100 Morrissey Blvd
    - Boston, Massachusetts, USA 02125
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: RJreferences.bib

---

@@

load(file = here('tabs/filerequirements.RData'))
```

@@

The required data files for using \CRANpkg{MassWateR} are shown in Table \@ref(tab:`r ifelse(knitr::is_html_output(), 'filreqhtml', 'filreqpdf')`), including the files that apply to the workflow steps in Figure \@ref(fig:workflow).  The files are each imported into R using specific `read` functions with relevant checks, explained in the next section.  These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a formatting issue.  The largest input file required for all parts of the workflow in Figure \@ref(fig:workflow) is the results file.  This file includes all water quality monitoring data to be used with the package. As such, the formatting requirements are the most burdensome for potential users and additional functions are available to assist with formatting.

```{r filreqhtml, eval = knitr::is_html_output()}
filerequirements
```
```{r filreqpdf, eval = knitr::is_latex_output(), results = 'asis'}
flextable_to_rmd(filerequirements)
```

>>>>

---
title: "MassWateR: Improving quality control, analysis, and sharing of water quality data"
date: "`r Sys.Date()`"
abstract: >
  An abstract of less than 150 words.
draft: true
author:  
  # see ?rjournal_article for more information
  - name: Marcus W. Beck
    affiliation: Tampa Bay Estuary Program
    address:
    - 263 13th Ave S
    - St. Petersburg, Florida, USA 33701
    url: https://tbep.org
    orcid: 0000-0002-4996-0059
    email:  mbeck@tbep.org
  - name: Benjamen Wetherill
    url: https://www.acasak.com/
    email: bwetherill@acasak.co
    affiliation: ACASAK Consulting
    address:
    - Boston, Massachusetts, USA
    orcid: 0000-0002-0912-0225
  - name: Jillian Carr
    url: https://www.mass.gov/orgs/massachusetts-bays-national-estuary-partnership
    email: Jillian.Carr@umb.edu
    affiliation: Massachusetts Bays National Estuary Partnership
    address:
    - University of Massachusetts Boston, 100 Morrissey Blvd
    - Boston, Massachusetts, USA 02125
  - name: Pamela DiBona
    url: https://www.mass.gov/orgs/massachusetts-bays-national-estuary-partnership
    email: pamela.dibona@state.ma.us
    affiliation: Massachusetts Bays National Estuary Partnership
    address:
    - University of Massachusetts Boston, 100 Morrissey Blvd
    - Boston, Massachusetts, USA 02125
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: RJreferences.bib
preamble: |
  \usepackage{multirow}
  \usepackage{multicol}
  \usepackage{colortbl}
  \usepackage{hhline}
  \newlength\Oldarrayrulewidth
  \newlength\Oldtabcolsep
  \usepackage{longtable}
  \usepackage{array}
  \usepackage{hyperref}
  \usepackage{float}
  \usepackage{wrapfig}\usepackage{longtable}
---

@@

add_latex_dep()
load(file = here('tabs/filerequirements.RData'))
```

@@

The required data files for using \CRANpkg{MassWateR} are shown in Table \@ref(tab:filereq), including the files that apply to the workflow steps in Figure \@ref(fig:workflow).  The files are each imported into R using specific `read` functions with relevant checks, explained in the next section.  These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a formatting issue.  The largest input file required for all parts of the workflow in Figure \@ref(fig:workflow) is the results file.  This file includes all water quality monitoring data to be used with the package. As such, the formatting requirements are the most burdensome for potential users and additional functions are available to assist with formatting.

```{r filreq}
filerequirements
```

### 2023-07-09 paper.tex
flextable issue fixed by adding latex dependencies

@@

@@

@@

>>>>

\ascline{1.5pt}{666666}{1-6}\endfirsthead \caption[]{\textcolor[HTML]{000000}{\fontsize{9}{11}\selectfont{File\ requirements\ for\ using\ MassWateR.\ \ Check\ marks\ indicate\ which\ file\ is\ required\ for\ each\ part\ of\ the\ MassWateR\ workflow.}}}\label{tab:filreqpdf}\\

@@

\ascline{1.5pt}{666666}{1-5}\endfirsthead

@@

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-|>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1.5pt}-}\endfirsthead

@@

\ascline{1.5pt}{666666}{1-6}\endfirsthead \caption[]{Field\ Blanks}\label{tab:unnamed-chunk-10}\\
